%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
\usepackage[T1]{fontenc}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Kapa}{Kudaibergenov}{ \urlstyle{same}\href{https://www.kaggle.com/kapakudaibergenov}{Kaggle} | \href{https://github.com/kudkapa59}{Github}\\
\href{mailto:kudkapa59@gmail.com}{kudkapa59@gmail.com} | +420775333602 | \href{https://www.linkedin.com/in/kapa-kudaibergenov/}{LinkedIn}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education} 

\subsection{CTU}
\descript{Bc. in Electrical Engineering and Computer Science}
\location{by Sept 2021 | Prague, Czech Republic}
Faculty of Electrical Engineering \\
%Magna Cum Laude\\
\location{ Avg. GPA: 1.39} %\\
%Major GPA: 3.9 / 4.0}
\sectionsep
\subsection{Gymnasium 4}
\location{Grad. May 2016|  Aktau,Kazakhstan}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Undergraduate}
Pattern recognition and Machine learning\\
Cybernetics and Artificial intelligence\\
Programming Algorithms\\
Probability and Statistics\\
Signal Theory
\sectionsep

\subsection{On-line}
Intro to Machine Learning - Coursera\\
Introduction to Deep Learning - MIT 6.S191\\
Inferential Statistics - Udemy\\
Intermediate Machine Learning - Kaggle\\
Natural Language Processing - Kaggle\\
Data Visualization - Kaggle\\
Intro to SQL - Kaggle\\
{\footnotesize \textit{\textbf{(working with BigQuery) }}} \\
Fundamentals of Git - Stepik\\
%{\footnotesize \textit{\textbf{(Research Asst. \& Teaching Asst 2x) }}} \\


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Proficient with:}
Python \textbullet{}  Microsoft Excel\textbullet{} SQL\textbullet{} \\
Linux \textbullet{} Git \textbullet{}\\ 
\location{Good with:}
C++ \textbullet{} HTML \textbullet{} Matlab \textbullet{} \LaTeX\textbullet{} \\
\location{Familiar with:}
Javascript \textbullet{} R(learning) \textbullet{}  PowerBI(learning)\textbullet{}
\sectionsep

\subsection{Machine Learning}
Python libraries(scikit-learn,seaborn,tensorflow, plotly,pandas,matplotlib) \textbullet{}  Algorithms(XGBoost, Random Forest, Neural Networks)\textbullet{} 
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Technical Projects}

\runsubsection{Sudoku Solver}
\descript{| \href{https://github.com/kudkapa59/SudokuSolver}{Github}}
\location{Winter 2021 | Prague, Czech Republic}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Python program designed to solve any sudoku puzzles.
\item Implemented Backtracking Algorithm with the use of Object Oriented Programming and Unit Testing.
\end{tightemize}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{FEL, Czech Technical University}
\descript{| Assistant Engineer }
\location{Oct 2019 - Jan 2020 | Prague, Czech Republic}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
Databases: After the University course at the Department of Circuit Theory I had an opportunity to collaborate with the work staff. Thanks to them I had experience on creating a new project. The project consisted of ordering
audiofiles’ database of people with Parkinson and Multiple System Atrophy(MSA) in Matlab.\\
The technological implementation lay in an upgrade of the operational algorithms, which would substitute much work of the technician. I was consulting about the stridor caused by MSA with specialists at Neurologick´a klinika 1.
LF UK a VFN.
\sectionsep

\runsubsection{a&o Hostels}
\descript{| Front Desk Receptionist and Bartender}
\location{Jan 2018 – March 2018 | Prague, Czech Republic}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Customer Service: Responsible for providing a friendly atmosphere to guests entering the hotel. Implemented cash operations and was taking the payment in the form of cash and credit cards. At the same time, I had
experience of working as a bartender and was obliged to make cocktails, serving food and beverages.
\item Organizational Part: Had to meet touristic groups and allocate their rooms depending on their preferences. Due to experience of working in hotels, within one month of work I was leading a group of new receptionists.
\item Soft Skills: Most of the time I managed to communicate with people, who didn’t speak my language.
\item Time Management: Often had to work at night, so I have experience in working in hard conditions and different time of day.
\end{tightemize}
\sectionsep

\runsubsection{Panorama Hotel}
\descript{| Wait Staff}
\location{May 2017 - July 2017 | Prague, Czech Republic}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Customer Service: Working within an international group. Providing excellent wait service. Participating in designing the banquets for 200+ people.
\item Time Management: Working predominantly at breakfasts and lunches
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Needed to just comment awards sectiom, but deleted it


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PUBLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\section{Publications} 
%\renewcommand\refname{\vskip -1.5em} % Couldn't get this working from the .cls file
%\bibliographystyle{abbrv}
%\bibliography{publications}
%\nocite{*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LANGUAGES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Languages}

English{\footnotesize \textit{\textbf{(proficient) }}} \textbullet{}  Czech{\footnotesize \textit{\textbf{(good working knowledge) }}}\textbullet{} 
French{\footnotesize \textit{\textbf{(working knowledge) }}}\textbullet{}
Russian{\footnotesize \textit{\textbf{(native speaker) }}}\textbullet{}
Kazakh{\footnotesize \textit{\textbf{(native speaker) }}}\textbullet{} 
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     HOBBIES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Hobbies}
Psychology\textbullet{}  Martial Arts\textbullet{} Chess\textbullet{} Learning Languages\textbullet{}\\
\sectionsep

\end{minipage} 
\end{document}  \documentclass[]{article}
